%!TEX root = ../template.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% acknowledgements.tex
%% NOVA thesis document file
%%
%% Text with acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgements

%The acknowledgements. You are free to write this section at your own will.  However, usually it starts with the institutional acknowledgements (adviser, institution, grants, workmates, \ldots) and then comes the personal acknowledgements (friends, family, \ldots).

After this crucial step in my academic career, I would like to thank the following people for their help and support throughout this dissertation:
%Saraiva

First of all, I would like to express my sincere thanks to my supervisor and professor, João Saraiva, for the time, patience, knowledge, dedication, and motivation throughout this dissertation and for proposing the subject of this master's thesis. Without his guidance, I would not have solved the problems and challenges I have encountered along this journey.
%Rui

I would like to extend my sincere thanks to my co-supervisor, Rui Pereira, for his assistance at every stage of this thesis. Whose knowledge in  Green Computing was essential to developing the research questions and methodology of this dissertation. His feedback leads me to develop a better and more rigorous work, bringing my work to a higher level.

%Green lab
I would like to offer my special thanks to all the members of the Green Software Lab for the willingness to help with any issues I had during my master's thesis, especially Rui Calheno for the tremendous help provided.  

%Friends
Also, I am deeply grateful to my friends. Together, we made countless hours of stories, adventures, and memories. I want sincerely praise all the support and friendship during these years.

%Family
Last but not least, my appreciation also goes out to my family for their encouragement and support all through my studies. Especially to my mom, I'm grateful for her support and belief.